Merging Datasets Through Deep learning

### 2018-11-05 old/paper2018/datasets.tex
llncs stuff for eswc

\begin{figure}[htb]
    \centering
    \begin{subfigure}[t]{0.23\textwidth}
        \centering
        \includegraphics[width=.95\linewidth]{people_recall}
        \caption{Recall rate as a function of neighborhood size}
        \label{people_recall}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.95\linewidth]{people_distances}
        \caption{Mean negative distance as a function of neighborhood size}
        \label{modified_loss}
    \end{subfigure}
    \label{people_distances}
    \caption{Characteristics of people data}
\label{people_characteristics}
\end{figure}

\begin{figure}[htb]
    \centering
    \begin{subfigure}[t]{0.23\textwidth}
        \centering
        \includegraphics[width=.99\linewidth]{company_recall}
        \caption{Recall rate as a function of neighborhood size}
        \label{company_recall}
    \end{subfigure}%                                                                                                   
    ~
    \begin{subfigure}[t]{0.23\textwidth}
        \centering
        \includegraphics[width=.99\linewidth]{company_distances}
        \caption{Mean negative distance from anchor as a function of neighborhood size}
        \label{modified_loss}
    \end{subfigure}
    \label{company_distances}
    \caption{Characteristics of company data}
\label{company_characteristics}
\end{figure}

>>>>

\begin{figure}[htb]
    \subfloat[Recall rate as a function of neighborhood size\label{people_recall}]{% 
        \includegraphics[width=.5\linewidth]{people_recall}
    }
    ~ 
    \subfloat[Mean negative distance as a function of neighborhood size\label{modified_loss}]{%
        \includegraphics[width=.5\linewidth]{people_distances}
     }
    \label{people_distances}
    \caption{Characteristics of people data}
\label{people_characteristics}
\end{figure}

\begin{figure}[htb]
   \subfloat[Recall rate as a function of neighborhood size\label{company_recall}]{%
        \includegraphics[width=.5\linewidth]{company_recall}
   }
   ~
   \subfloat[Mean negative distance from anchor as a function of neighborhood size \label{modified_loss}]{%
        \includegraphics[width=.5\linewidth]{company_distances}
   }
    \label{company_distances}
    \caption{Characteristics of company data}
\label{company_characteristics}
\end{figure}
